---
title: "Overview"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Overview}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```
The goal of BAP is to calculate New York State Department of Environmental Conservation's Biological Assessment Profiles (BAPs). For more information please refer to the following fact sheet: https://www.dec.ny.gov/docs/water_pdf/bapnarrative18.pdf

## Installation

You can install the BAP package from [GitHub](https://github.com/) with the following code. You may need to install Rtools to build the package. __Rtools is not an R package. You must download Rtools from the following source:__ https://cran.r-project.org/bin/windows/Rtools/.

``` r
# install.packages("devtools")
devtools::install_github("DEC-SMAS/BAP")
```
## Example

This is a basic example to show you how to quickly calculate BAP scores.

```{r example}
library(BAP)
```

Import your dataset.
```{r}
taxa.df <- read.csv(file.path(here::here(),
                              "data",
                              "rif.csv"),
                              # "Mosher_Request_1_6_17.csv"),
                    stringsAsFactors = FALSE)

taxa.df$LOCATION <- ifelse(taxa.df$LOCATION %in% "MUDG_T71", "MUDG_T72", taxa.df$LOCATION)
"	0.3_MUDG_T71_ 4_7/18/2019_1"
taxa.df$EVENT_ID <- ifelse(taxa.df$EVENT_ID %in% "0.3_MUDG_T71_ 4_7/18/2019_1", "0.3_MUDG_T72_ 4_7/18/2019_1", taxa.df$EVENT_ID)
```

Prepare your dataset for processing.
```{r}
long.df <- data_prep(taxa.df)
long.df <- taxa.df
```

Calculate the BAP of interest.
```{r}
bap_multi.df <- bap_mp_nav_waters(Long = long.df)
bap_riffle(long.df)
```

```{r}
knitr::kable(bap_multi.df)
```

Export the results as a CSV.
```{r, eval=FALSE}
write.csv(bap_multi.df, 
          file.path(paste0(Sys.Date(), "_bap_multiplate", ".csv")))
```
